Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-07-26 GWLDCI.tex
minor rephrasing

The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have an outer edges between vertices 9 and 1, and between 5 and 8}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.  In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
\end{eg}

>>>>

The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have outer edges between vertices 8 and 9, 9 and 1, 4 and 5, and 5 and 8}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.  In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
\end{eg}
